Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-10-13 manuscript/supplement_motifs.tex
updated all with Kate's random effect

    Persistence varied with the frequencies of different motifs in a network profile.

    \begin{table}[h!]
        \caption{Coefficients ($\beta$) for models relating persistence to the proportion of a network profile, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction. Predictors were centered and scaled before model fitting. All effects were significant ($p$\textless0.001). We also provide the $R^2$. }
        \label{motif_profile_tab}
        \centering
        \begin{tabular}{c|c c c c c | c}
            Motif & Intercept & Proportion & Disturbance & Interaction & $R^2$\\
            \hline
            Omnivory & 0.572 & -0.0133 & -0.139 & -4.89$\times10^{-4}$ & 0.908 \\
            Apparent competition & 0.572 & 0.0105 & -0.139 & 4.78$\times10^{-4}$ & 0.905 \\
            Direct competition & 0.572 & 2.62$\times10^{-3}$ & -0.139 & 3.84$\times10^{-4}$ & 0.901 \\
            Three-species chain & 0.572 & 6.12$\times10^{-3}$ & -0.139 & -1.90$\times10^{-4}$ & 0.901 \\ 
        \end{tabular}
    \end{table}
\clearpage

\section{Motif profiles and global properties}

@@

    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/persistence_vs_SC_lm.eps}
        \caption{Persistence decreased strongly with increasing probability of disturbance to basal resources, while network size, connectance, and their interaction had smaller effects. \textbf{A)} Persistence decreased slightly with increasing network size at high levels of disturbance, increased slightly with increasing network size at low levels of disturbance, and did not vary noticeably with network size at moderate levels of disturbance. Networks with lower connectance (dotted line) had slightly higher persistence than networks with moderate (solid line) or high (dashed line) connectance.
        \textbf{B)} Persistence decreased with increasing connectance for all levels of disturbance and network size. Network size (line types) did not strongly affect these relationships.}
        \label{fig:lm_CS}
    \end{figure}

>>>>

    % Updated and expanded to include permanova tests
    Persistence varied with the frequencies of different motifs in a network profile ($F_{1,2998}$=645, $p$\textless0.001 for a PERMANOVA of dissimilarity in motif profiles against mean persistence).
    However, motif profiles were not evenly distributed across mean persistences ($F_{134,2865}$=1.77, $p$\textless0.001 for an ANOVA of dissimilarity in motif profiles against mean persistence, rounded to 3 decimal places).
    Specifically, motif profiles were more variable (higher dissimilarities) in networks with higher mean persistence.
    As non-homogeneous variability can cause a PERMANOVA to return a false positive~\citep{Anderson2001}, this means that we must treat our PERMANOVA result as tentative and place more weight on the single-motif regressions.

    % Updated to use mean instead of all species
    \begin{table}[h!]
        \caption{Coefficients ($\beta$) for models relating persistence to the proportion of a network profile, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction. Predictors were centered and scaled before model fitting. All effects were significant ($p$\textless0.05). We also provide the $R^2$ (multiple $R^2$). }
        \label{motif_profile_tab}
        \centering
        \begin{tabular}{c|c c c c c | c}
            Motif & Intercept & Proportion & Disturbance & Interaction & $R^2$\\
            \hline
            Omnivory & 0.574 & -0.0140 & -0.139 & -5.59$\times10^{-4}$ & 0.968 \\
            Apparent competition & 0.574 & 0.0112 & -0.139 & 5.90$\times10^{-4}$ & 0.964 \\
            Direct competition & 0.574 & 3.38$\times10^{-3}$ & -0.139 & 1.81$\times10^{-4}$ & 0.958 \\
            Three-species chain & 0.574 & 5.80$\times10^{-3}$ & -0.138 & -3.07$\times10^{-5}$ & 0.960 \\ 
        \end{tabular}
    \end{table}
\clearpage

\section{Motif profiles and global properties}
% No update needed

@@

    % updated to use network means rather than all species
    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/persistence_vs_SC_lm.eps}
        \caption{Persistence decreased strongly with increasing probability of disturbance to basal resources, while network size, connectance, and their interaction had smaller effects. \textbf{A)} Persistence decreased slightly with increasing network size at high levels of disturbance, increased slightly with increasing network size at low levels of disturbance, and did not vary noticeably with network size at moderate levels of disturbance. Networks with lower connectance (dotted line) had slightly higher persistence than networks with moderate (solid line) or high (dashed line) connectance.
        \textbf{B)} Persistence decreased with increasing connectance for all levels of disturbance and network size. Network size (line types) did not strongly affect these relationships.}
        \label{fig:lm_CS}
    \end{figure}
